A DPG method for compressible flow problems

### 2012-06-20 docs/Jesse/Proposal/proposalIntro.tex
adding changes to proposal

\section{Range of CFD problems}

\begin{figure}[!h]
\centering
\includegraphics[scale=.45]{figs/CFD_tree.pdf}
\caption{A diagram of common CFD problems and their simplifying assumptions.}
\end{figure}

\begin{itemize}
\item Discuss full compressible Navier-Stokes with boundary layers
\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
\item Discuss model problems
\end{itemize}

>>>>

%\section{Range of CFD problems}
%
%\begin{figure}[!h]
%\centering
%\includegraphics[scale=.45]{figs/CFD_tree.pdf}
%\caption{A diagram of common CFD problems and their simplifying assumptions.}
%\end{figure}
%
%\begin{itemize}
%\item Discuss full compressible Navier-Stokes with boundary layers
%\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
%\item Discuss model problems
%\end{itemize}
